%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.3 (04/10/2018)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% Modified author:
% Ajay Kumar Nelavagilu Udaya Kumar 
%
% Modified author repository:
% https://github.com/AjayKumar4/AJ-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{aj-resume-openfont}

\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{}{Assumpta Pinto} {\urlstyle{same} 
\href{https://www.linkedin.com/in/assumpta-pinto}{\linkedinsocialsymbol{} assumpta-pinto} |
\href{mailto:asumpret@gmail.com}{\emailsymbol{}asumpret@gmail.com} | 
\mobilephonesymbol{}+353 894875512 \linebreak \locationsymbol{}\address{Galway, Ireland}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Trinity College Dublin}
\descript{Master’s in Philosophy - International Peace Studies}
\location{Oct 2020 | Dublin, Ireland} 
\sectionsep

\subsection{Xavier Institute of Management and Entrepreneurship}
\descript{Master’s in Business Management - Marketing and Human Resources}
\location{Apr 2017 | Bengaluru, India} 
\sectionsep

\subsection{Visveswaraya Technological University}
\descript{Bachelor’s in Computer Science and Engineering}
\location{June 2015 | Belguam, India} 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{CERTIFICATIONS} 
\highlighttext{Digital Security and Human Rights} \newline 
{\footnotesize \textit{\textbf{(Amnesty International) }}} \newline 
\highlighttext{Positive Peace Academy} \newline 
{\footnotesize \textit{\textbf{(Institute of Economics and Peace) }}} \newline
\highlighttext{Conflict Series, Confronting Trauma, Gender Matters , Youth and Peacebuilding, Environment, Natural Resources and UN Peacekeeping Operations } \newline 
{\footnotesize \textit{\textbf{(United Nations Institute Of
Training And Research) }}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     KEY COMPETENCIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{KEY COMPETENCIES} 
\textbullet{} Adaptable
\textbullet{} Analytical
\textbullet{} Attention to Detail
\textbullet{} Curious
\textbullet{} Creative
\textbullet{} Empathetic
\textbullet{} Entrepreneurial
\textbullet{} Observant\newline 
\textbullet{} Quick-Learner 
\textbullet{} Result-Oriented
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Technical Skills}
\textbullet{}Salesforce
\textbullet{}WordPress
\textbullet{}Wix
\textbullet{}Shopify
\textbullet{}Canva
\textbullet{}Buffer
\textbullet{}Zoho
\textbullet{}CRM
\textbullet{}SEO/SEM
\textbullet{}Social Media
\textbullet{}Microsoft Word
\textbullet{}Excel
\textbullet{}PowerPoint
\textbullet{}Phone \& Email
\sectionsep
\subsection{Personal Skills}
\textbullet{} Public Speaking 
\textbullet{} Relationship Building
\textbullet{} Fundraising
\textbullet{} Leadership
\textbullet{} Negotiation
\textbullet{} Communication
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{\href{https://www.infosysbpm.com}{Infosys BPM }}
\descript{| Process Advisor }
\location{ Feb 2021 – Present | Galway, Ireland}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Specialised as a \highlighttext{Subject Matter Expert} (SME).
\item \highlighttext{Customer-facing role} in a dynamic, high-pressured, time bound environment which requires \highlighttext{adept problem-solving} to provide long term solutions, while simultaneously \highlighttext{collaborating} with other teams.
\item Understand the customer and the situation, while focusing on \highlighttext{de-escalating} matters and effectively negotiating best options for stakeholders.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://faithhopelovemovement.com}{Faith. Hope. Love. Movement}}
\descript{| Founder and Editor }
\location{Mar 2018 – Present | Galway, Ireland}
\begin{tightemize}
\item \highlighttext{Developing content and designs} for a Christian faith-based website across multiple online and offline platforms.
\item \highlighttext{Moderating and designing} content curated by other writers while managing their submissions.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://purpletag.ie}{PurpleTag }}
\descript{| Customer Service Executive }
\location{ Oct 2019 – Feb 2020 | Dublin, Ireland}
\begin{tightemize}
\item \highlighttext{Handled deliverables} in a fast-paced, time bound environment.
\item Responded to \highlighttext{customer queries} and \highlighttext{grievances} via email. 
\item Worked on\highlighttext{improving the content} of the website and \highlighttext{SEO/SEM}.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://www.amazon.in}{Amazon}}
\descript{| Onboarding Account Specialist }
\location{June 2018 – Aug 2019 | Bengaluru, India}
\begin{tightemize}
\item Specialized in \highlighttext{Pay-per-Click (PPC)} and banner \highlighttext{advertisements} on Amazon’s platform; KPIs included account activation and onboarding.
\item As a consultant for advertising, educated and launched sellers in the Indian marketplace on “Sponsored Products” and “Sponsored Brands” ad campaigns and assisted them in achieving their \highlighttext{business goals}.
\item Single-handedly \highlighttext{managed, optimized and maintained} over 500+ accounts across different categories of products for various brands
\item Focused \highlighttext{relationship management, retention} and \highlighttext{account optimization} while actively engaged in client retention.
\item Actively worked as a \highlighttext{tester} for the development team, for new-to-market tool launches.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://www.cpgroupglobal.com}{Charoen Pokphand Group}}
\descript{| Business Management Trainee }
\location{July 2017 – Nov 2017 |  Bangkok, Thailand}
\begin{tightemize}
\item Trained in different business units under the CP conglomerate and reported business progress directly to the top management regularly
\item Achieved observable \highlighttext{process improvement} in True Corporation and 7-Eleven while streamlining service and preserving highest levels of customer service.
\item Successfully managed \highlighttext{end-to-end process} of a new business- ‘Papa’s Burger’ through strategic management, product and service marketing, HRM, sales, \highlighttext{project and resource management}, delivery
and analytics. Promoted the brand and succeeded in achieving breakeven in 8 months of establishment.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://www.arcesium.com}{Arcesium}}
\descript{| Human Capital Intern }
\location{May 2016 – June 2016 | Hyderabad, India}

\end{minipage} 
\end{document}  \documentclass[]{article}